Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-20 manuscript.Rmd
More updates to figures.

>>>>

bigList <- left_join(n.so, n.yr) %>%
    group_by(title, year) %>%
    summarize(N = n())
bigList$shortTitle <- abbreviate(bigList$title)

ggplot(bigList, aes(year, N, group = 1)) + geom_line(colour="#5e3c99") + 
    facet_wrap(~ title, ncol=7) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), 
panel.grid.minor = element_blank(), 
    axis.text.x = element_text(angle=45, hjust=1, size =8)) + 
    scale_x_discrete(breaks=seq(1989, 2013, 5)) + 
    ylim(0, 150)
